A dataset of every book, article, or pamphlet Marx is known have read ($N \approx 1800$), as scraped from a variety of sources:
\begin{itemize}
    \item \textit{MEGA}² Abteilung IV, containing 31 volumes of Marx's and Engels' notes and excerpts, plus a volume (IV/32) listing every book known to have existed in their respective personal libraries.
    \item The IISH's listing of Marx's and Engels' notebooks, which comes out to 168 notebooks total, some of which have yet to be published in volumes of \textit{MEGA}² Abteilung IV. This listing is available via the IISH website, at \url{https://search.iisg.amsterdam/Record/ARCH00860/ArchiveContentList#A072e534c62}
    \item \cite{rubel_les_1957}, \cite{rubel_les_1960}, \cite{rubel_marx_1975}, and \cite{rubel_marx_1980}
    \item Additional summary information given in the published volumes of \justoldmega{}.
\end{itemize}

\noindent The full dataset is available at \href{https://airtable.com/shrDmaEAV4gKDB2n2}{https://airtable.com/shrDmaEAV4gKDB2n2}.

%, password ``\texttt{mega2021

\subsection*{Reading Notebooks Sample}

As a fairly representative example, \oldmega{I}{3} gives the following information on Marx's Parisian excerpt notebooks of Oct 1843--1844 (Described on pages 411--416 of the volume):

\begin{enumerate}
    \item Pierre le Pesant de \textsc{Boisguillebert}, \textit{Le detail de la France, la cause de la diminution de ses biens, et la facilité du remède}. In dem Sammelwerk: \textit{Économistes financiers du XVIIIe siècle. Herausgegeben und erläutert von Eugène Daire.} Paris 1843. p. 171--266.
    
    Heft VIII. 4½ S. --- 38 kurze und mittlere Exzerpte, größerenteils französisch.
    
    (Notebook VIII. 4½ pages. --- 38 short and medium excerpts, mostly in French.)
    
    (Reproduced in \oldmega{I}{3}{563--568}.)
    
    \item Pierre le Pesant de \textsc{Boisguillebert}, \textit{Dissertation sur la nature des richesses, de l'argent et des tributs}. In demselben Sammelwerk, p. 394--424.
    
    Heft VIII. 10¼ S. --- 50 kurze und mittlere Exzerpte, größerenteils französisch --- Von Marx: 1 Glosse über Geld und Wert; ferner 1 größere Glosse über Überproduktion.
    
    (Notebook VIII. 10¼ pages. --- 50 short and medium excerpts, mostly in French --- From Marx: 1 gloss on money and value and 1 major gloss on overproduction.)
    
    (Reproduced in \oldmega{I}{3}{568--579}.)
    
    \item Pierre le Pesant de \textsc{Boisguillebert}, \textit{Traité de la nature, culture, commerce et intérêt des grains.} In demselben Sammelwerk, p. 352--393.
    
    Heft VIII. 4 S. --- 38 kurze und mittlere Exzerpte, größerenteils französisch.
    
    (Notebook VIII. 4 pages. --- 38 short and medium excerpts, mostly in French)
    
    (Reproduced in \oldmega{I}{3}{579--583}.)
    
    \item Eugene \textsc{Buret}, \textit{De la misère des classes laborieuses en Angleterre et en France}. T. I--II. Paris 1840. VI, 432 p. 492 p.
    
    Heft IX. 24 S. --- 41 teils mittlere, teils lange Auszüge, umfassend T. I, deutsch, mit nur wenigen wörtlichen französischen Exzerpten. --- Von Marx: 2--3 kleine Zwischenbemerkungen.
    
    (Notebook IX. 24 pages. --- 41 partly medium, partly long excerpts, all from T. I, in German, with only a few verbatim French excerpts. --- From Marx: 2--3 small interim remarks.)
    
    \item A.-L.-C. \textsc{Destutt de Tracy}, \textit{Éléments d'idéologie. IVe et Ve parties. Traité de la volonté et de ses effets.} Paris 1826. XII, IV, 401 p.
    
    Heft V. 3 S. --- Ein längeres Exzerpt, bestehend aus 29 Teilstücken aus der IVe partie, teils französisch, teils deutsch; ein kürzeres Exzerpt vom Schluß (Extrait raisonné) der Ve partie, deutsch.
    
    (Notebook V. 3 pages. --- A longer excerpt, consisting of 29 quotations from Part IV, partly French, partly German; A shorter excerpt from the conclusion (Extrait raisonne) of Part V, German.)
    
    (Reproduced in \oldmega{I}{3}{560--563}.)
    
    \item Friedrich \textsc{Engels}, \textit{Umrissie zu einer Kritik der Nationalökonomie}. In: \textit{Deutsch-Französische Jahrbücher} 1844. p. 86--114.
    
    Heft V. ½ S. (auf losem Blatt eingefügt). --- Ein mittlerer und em kürzerer Auszug, deutsch.
    
    (Notebook V. ½ page. (Inserted on loose sheet). --- A medium and a short excerpt, German.)
    
    (Reproduced in \oldmega{I}{3}{437}.)
    
    \item James \textsc{Lauderdale}. \textit{Recherches sur la nature et l'origine de la richesse publique. Traduit par E. Lagentie de Lavaïsse.} Paris 1808. XXVII, 344 p.
    
    Heft VI. 16 S. --- 87 größtenteils mittlere Exzerpte, das ganze Werk (ohne Supplément) umfassend, teils französisch, teils deutsch.
    
    (Notebook VI. 16 pages. --- 87 mostly medium excerpts, covering the whole work (without supplement), partly in French, partly in German.)
    
    \item Jean \textsc{Law}, \textit{Considérations sur le numéraire et le commerce.} In dem Sammelwerk: \textit{Économistes financiers du XVIIIe siecle}. Herausgegeben und erläutert von Eugène Daire. Paris 1843. p. 465--548.
    
    Heft VIII. 1 S. --- 9 kleinere Auszüge aus Chap. I und II, größtenteils deutsch.
    
    (Notebook VIII. 1 page. --- 9 smaller excerpts from Chap. I and II, mostly German.)
    
    \item R. \textsc{Levasseur (de la Sarthe)}, \textit{Ex-Conventionnel. Mémoires.} T. I--II. Paris 1829. T. III—IV. Paris 1831, 392 p. 386 p. 352 p. 377 p.
    
    Heft III. 5 S. --- 43 meist kurze Exzerpte aus T. I, französisch, auf der linken Spalte des Manuskripts; hierzu auf der rechten Spalte eirie Art Konspekt, deutsch.
    
    (Notebook III. 5 pages. --- 43 mostly short excerpts from T. I, French, in the left column of the manuscript; on this in the right column eirie Art Konspekt, German.)
    
    (Reproduced in \oldmega{I}{3}{417--434}.)
    
    \item Friedrich \textsc{List}, \textit{Das nationale System der politischen Ökonomie. 1. Band: Der Internationale Handel, die Handelspolitik und der deutsche Zollverein}. Stuttgart u. Tübingen 1841. LXVIII, 589 p.
    
    Heft VII. 17 S. (halbbrüchig). --- 42 zumeist mittlere und längere Exzerpte aus dem 1. und 2. Buch, deutsch. --- Von Marx: Kleine Glosse über die Listsche Werttheorie.
    
    (Notebook VII. 17 pages. (Half-broken). --- 42 mostly medium and long excerpts from the 1st and 2nd book, in German. --- From Marx: Small gloss on List's theory of value.)
    
    \item John Ramsay \textsc{MacCulloch}, \textit{Discours sur l'origine, les progrès, les objets particuliers et l'importance de l'économie politique. Traduit de l'anglois par G. Prevost}. Genève et Paris 1825. XVI, 204 p.
    
    Heft V. 9 S. --- 41 kurze und mittlere Exzerpte aus dem Hauptteil und den Réfelexions du traducteur sur le système de Ricardo. --- Von Marx: 3 kleine Bemerkungen über Grundeigentum, Ricardosche Schule, Preis und Produktionskosten, ferner 1 Ausführung über Produktionskosten und Preis und 1 Zusammenfassung über Profit.
    
    (Notebook V. 9 pages. --- 41 short and medium excerpts from the main part and the reflections of the translator of Ricardo's system. --- From Marx: 3 small remarks on real estate, Ricardo's school, price and production costs, also 1 discussion of cost and price and 1 summary of profit.)
    
    (Reproduced in \oldmega{I}{3}{550--560}.)
    
    \item James \textsc{Mill}, \textit{Elements d'économie politique. Traduit par J. T. Parisot}. Paris 1823. VII, 318 p.
    
    Heft IV. 17 S. --- 52 meist kurze und mittlere Exzerpte, in dichter Folge den ganzen Band bis auf die zweite Hälfte von Chap. IV umfassend, größtenteils deutsch. --- Von Marx: 1 längere Ausführung uber Geld, Kreditsystem, Austausch, Gemeinwesen, Privateigentum, Tausch, Preis, Arbeit; ferner 1 längere Ausführung über Austausch auf der Basis des Privaleigentums.
    
    (Notebook IV. 17 pages. --- 52 mostly short and medium excerpts, closely following the whole volume except for the second half of Chap. IV, mostly in German. --- From Marx: 1 longer discussion of money, the credit system, exchange, community, private property, exchange, price, labor; also 1 longer discussion of exchange on the basis of private property)
    
    (Reproduced in \oldmega{I}{3}{520--547}.)
    
    Heft V. 6 S. --- 10 zumeist mittlere Exzerpte aus der zweiten Hälfte von Chap. IV, sämtlich deutsch. --- Von Marx: 1 kleine Glosse über Grundrente als einzige Steuerquelle.
    
    (Notebook V. 6 pages. --- 10 mostly medium-length excerpts from the second half of Chap. IV, all in German. --- From Marx: 1 small gloss on land rent as the only source of tax.)
    
    (Reproduced in \oldmega{I}{3}{547--550}.)
    
    \item H. F. \textsc{Osiander}, \textit{Enttäuschung des Publikums über die Interessen des Handels, der Industrie und der Landwirtschaft, oder Beleuchtung der Manufakturkraft Philosophie des Dr. List, nebst einem Gebet aus Utopien}. Tübingen 1842. X, 228 p.
    
    Heft VII. Über die rechte Spalte von 12 S. verstreut, den Exzerpten aus Friedr. List gegenübergestellt, 13 längere u. kürzere Teilstücke, enlhaltend insgesamt 29 kurze Exzerpte, deutsch.
    
    (Notebook VII. Scattered over the right column of 12 pages, the excerpts from Friedrich List are juxtaposed, in 13 longer and shorter sections, for a total of 29 short excerpts, in German.)
    
    \item H. F. \textsc{Osiander}, \textit{Über den Handelsverkehr der Völker}. Bd. I--II. Stuttgart 1840. X, 309 p. 318 p.
    
    Heft VII. 1 S. --- 4 kürzere Exzerpte aus Kap. 1--3 des 1. Bandes, deutsch.
    
    (Notebook VII. 1 page. --- 4 shorter excerpts from chap. 1--3 of Volume 1, in German.)
    
    \item David \textsc{Ricardo}, \textit{Des principes de l'économie politique et de l'impôt. Traduit par F.-S. Constancio}. Seconde édition. T. I--II. Paris 1835. XL, 378 p. 328 p.
    
    Heft IV. 17 S. --- 53 meist kurze uud mittlere Exzerpte, umfassend T. I, teils deutsch, teils französisch; 27 kurze und mittlere Exzerpte, T. II umfassend, größtenteils deutsch. --- Von Marx; Etwa 15 kleine Bemerkungen; ferner 1 Glosse über Konkurrenz der Kapitalien, 1 Glosse über revenu brut et net und die Infamie der Nationalökonomie, 1 Glosse über Zynismus Ricardos und Verwendung der Kapitalien.
    
    (Notebook IV. 17 pages. --- 53 mostly short and medium excerpts from T. I, partly in German, partly in French; 27 short and medium comprehensive excerpts from T. II, mostly in German. --- From Marx: About 15 small remarks; 1 gloss on competition of capital, 1 gloss on gross and net income and the infamy of economics, 1 gloss on Ricardo's cynicism and the use of capital.) 
    (Reproduced in \oldmega{I}{3}{493--519}.)
    
    Heft VII. 1 S. --- Ein längeres Exzerpt aus T. II, Chap. XXVII (De la monnaie et des banques), durchaus französisch (außer dem letzten Satz).
    
    (Notebook VII. 1 page. --- A longer excerpt from T. II, Chap. XXVII (De la monnaie et des banques), entirely in French (except for the last sentence).)
    
    \item Jean-Baptiste \textsc{Say}, \textit{Traité d'économie politique}, Troisième édition. T. I-II. Paris 1817. LXXIX, 452 p. 486 p.
    
    Heft I. 21 S. --- 218 kurze Exzerpte, hiervon: 86 Stücke aus T. I, fast den ganzen Band umfassend, größtenteils französisch; 132 Stücke aus T. II, fast den ganzen Band umfassend, ausnahmslos französisch. --- Von Marx: 1 kleine Glosse über Stellung der Nationalökonomie zum Privateigentum und über Reichtum.
    
    (Notebook I. 21 pages. --- 218 short excerpts: 86 from T. I, covering nearly the entire volume, mostly in French; 132 from T. II, also covering nearly the entire volume, all in French. --- From Marx: 1 small gloss on the perspective of economics on private property and on wealth.)
    
    (Reproduced in \oldmega{I}{3}{437--455}.)
    
    \item Jean-Baptiste \textsc{Say}, \textit{Cours complet d'économie politique pratique}. Troisième édition. Bruxelles 1836. XIII, 746 p.
    
    Heft I. ¼ S. --- 3 kurze Exzerpte aus den \textit{Considérations générales}, französisch.
    
    (Notebook I. ¼ page. --- 3 short excerpts from the \textit{Considérations générales}, in French.)
    
    (Reproduced in \oldmega{I}{3}{455}.)
    
    \item Carl Wolfgang Christoph \textsc{Schüz}, \textit{Grundsätze der National-Ökonomie.} Tübingen 1843. XVI, 448 p.
    
    Heft VII. 1 S. --- 14 kurze Exzerpte aus dem größten Teil des Bandes, deutsch.
    
    (Notebook VII. 1 page. --- 14 short excerpts from most of the volume, in German.)
    
    \item Frédéric \textsc{Skarbek}, \textit{Théories des richesses sociales.} T. I-II. Paris 1829. 352 p. 324 p.
    
    Heft I. 2¼ S. --- 24 kurze Exzerpte aus T. I, Introduction, livre I und II, sämtlich französisch.
    
    (Notebook I. 2¼ pages. --- 24 short excerpts from T. I, the Introduction, books I and II, all in French.)
    
    (Reproduced in \oldmega{I}{3}{455--456}.)
    
    \item Adam \textsc{Smith}, \textit{Recherches sur la nature et les causes de la richesse des nations. Traduction nouvelle par Germain Garnier}. T. I--V. Paris 1802. CXXXVII, 368 p. 493 p. 564 p. 556 p. 588 p.
    
    Heft II. 23 S. --- 100 fast durchaus kürzere und mittlere Exzerptstücke, teils französisch, teils deutsch, in folgender Anordnung: 57 Stücke aus T. 1. livre 1, Chap. I--VII; 9 kurze Stücke aus T. II, livre II, Chap. II; 18 Stücke aus T. I, von Chap. VIII bis Schluß; 15 Stücke aus T. II, von livre I, Chap. XI bis Schluß von livre II; 1 mittleres Exzerpt aus T. I, livre I, Chap. X. --- Von Marx: 1 kurze Glosse über Smiths Erklärung von Tausch und Arbeitsleistung; ferner mehrere kleine Zusammenfassungen.
    
    (Notebook II. 23 pages. --- 100 almost entirely short and medium-sized excerpts, some in French, some in German, in the following arrangement: 57 from T. 1. livre 1, Chap. I--VII; 9 short excerpts from T. II, livre II, Chap. II; 18 from T. I, from Chap. VIII to the end; 15 from T. II, livre I, Chap. XI to the end of livre II; 1 medium excerpt from T. I, livre I, Chap. X. --- From Marx: 1 short gloss on Smith's explanation of exchange and labor; also several small summaries.)
    
    (Reproduced in \oldmega{I}{3}{457--477}.)
    
    Heft III. 11 S. --- 73 kurze und mittlere Exzerpte, teils französisch, teils deutsch; hiervon: 30 Stücke aus T. II, von Beginn des livre III bis Bandschluß; 43 Stücke aus T. III, den ganzen Band umfassend (mit größeren Lücken). --- Von Marx: kleine Zwischenbemerkung.
    
    (Notebook III. 11 pages. --- 73 short and medium excerpts, some in French, some in German; of these: 30 from T. II, from the beginning of livre III to the end of the volume; 43 from T. III, across the whole volume (with large gaps). --- From Marx: small interim remark.)
    
    (Reproduced in \oldmega{I}{3}{477--492}.)
    
    \item \textsc{Xenophon}'s von Athen \textit{Werke. Übersetzt von Adolph Heinrich Christian}. Bd. IX: \textit{Von der Haushaltungskunst und Hiero oder Herrscherleben.} Stuttgart 1828. p. 1041--1187. Bd. X: \textit{Staatsverfassung der Lacedämonier; Staatsverfassung der Athener etc.} Stuttgart 1830. p. 1193 bis 1323. Bd. XI: \textit{Von den Staatseinkünften der Athener, etc.} Stuttgart 1830. p. 1329--1458.
    
    Heft IV. 1½ S. --- 6 kurze Exzerpte aus Staatsverfassung der Lacedämonier, 5 aus Staatsverfassung der Athener, 1 aus Staatseinkünfte der Athener, 4 aus Haushaltungskunst, 1 aus Hiero, sämtlich deutsch. Ohne Bezeichnung der benützten Ausgabe und ohne Seitenangaben.
    
    (Notebook IV. 1½ pages. --- 6 short excerpts from the state constitution of the Lacedämonier, 5 from the state constitution of the Athenians, 1 on state income of the Athenians, 4 on household arts, 1 from Hiero, all in German. No description of the edition used and no page numbers.)

\end{enumerate}


