A dataset with the full (German, if available, otherwise original-language) text of every known piece of writing of Marx, $N \approx 1200$ excluding letters, or $N \approx 5200$ including letters.

\subsubsection{The Marx-Engels Digital Register}

The dataset of $N \approx 1200$ writings (excluding letters) is available at \href{https://airtable.com/shrFKP7fp64su32Ad}{https://airtable.com/shrFKP7fp64su32Ad}.

As a small sample to illustrate the contents of the \textit{Digital Register}, the first and last 10 entries for Marx (by Register code) are reproduced below. Note that, for the sake of brevity, metadata on the texts' translations are only included for the first entry in which this information exists (\textbf{M1}) and omitted thereafter. Similarly, metadata on known reprints are only included for the first entry in which this information exists (\textbf{M3}) and omitted thereafter. ``\{Dubiosa \& Apocrypha\}'' in the entry's title denotes that the attribution of this text to Marx is dubious or has been shown to be erroneous. ``[Untitled]'' in the entry's title denotes that the text was not given a title by Marx or by his editors, so that a title has been created by the Center for Socialist History for ease of reference.

%\subsubsection*{First 15}
\subsubsection*{First 10}

\begin{itemize}
    \item \textbf{M1}: \textit{Abolitionist rallies in America}.
    \begin{itemize}
        \item Original Language: German
        \item Title in Original Language: \textit{Abolitionistische Kundgebungen in Amerika}.
        \item Date of Writing: 1862 Aug 22.
        \item Date of Publication: Aug 30, in \textit{Die Presse}. N/s.
        \item Source: \MEW{15}{530-533}.
        \item Translations: \register{ST/ME10c} (CWUS) 201 (``Abolitionist demonstrations''); \register{ST/M79} (Pad/2) 215 (same title).
        \item Additional Info: M's article is largely devoted to reporting a speech by Wendell Phillips; within quotes he offers a mixture of quotations and summaries. \register{ST/ME10c} solves the problem by leaving out the quote marks altogether; \register{ST/M79}, by dropping M's text for Phillips' own words (from his book).
        \item Digital Chronicle references: \chron{62}{42}.
    \end{itemize}
    
    \item \textbf{M2}: [This number canceled, by authors of original \textit{Marx-Engels Register}]
    
    \item \textbf{M3}: \textit{Achievements of the ministry}.
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1853 Apr 12.
        \item Published: Apr 27, in \textit{NYDT}, \#3753, p. 5ef, under the rubric ``England.'' Signed.
        \item Source: \MECW{12}{50}.
        \item Reprinted: \%\register{ST/M80} (Pad/6)
        \item Additional Info: In \MEW{9}{49-55}.
        \item Digital Chronicle references: \chron{53}{15}.
    \end{itemize}
    
    \item \textbf{M4}: \textit{The acquittal of Simon Bernard}. [Untitled] \{Dubiosa \& Apocrypha\}
    \begin{itemize}
        \item Original Language: English
        \item Published: 1858 May 3, in NYDT, p. 4cde. Lead article; n/s.
        \item Additional Info: Listed by Rubel; rejected by IML, not in \textit{MEW}. This, as well as \register{M945}, was clearly written in NY; in my opinion there is no possibility of M's authorship.
    \end{itemize}

    \item \textbf{M5}: \textit{Address from the Working Men’s International Association to President Johnson. To Andrew Johnson, President of the United States}.
    \begin{itemize}
        \item Original Language: English
        \item Written: 1865 May 2-9; adopted by the GC May 9. Signed by the GC.
        \item Dated: May 13.
        \item Published: May 20, in the \textit{Bee-Hive}; May 21, in \textit{Reynolds's Newspaper}; June 1, in \textit{NYDT}.
        \item Source: \textit{GCFI} 1:294.
        %\item Reprinted: ST/ME10c (CWUS) 283; ST/M79 (Pad/2) 241; ST/M85 (Pad/3) 20.
        \item Additional Info: In \MEW{16}{98-99}. The name for the IWMA used in this title was soon dropped.
        \item Digital Chronicle references: \chron{65}{32}.
    \end{itemize}

    \item \textbf{M6}: \textit{Address of the British Federal Council to the sections, branches, affiliated societies and members}.
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1872 Dec 23.
        \item Published: Dec 31, as a flysheet, signed by the Council.
        \item Additional Info: In \MEW{18}{202-207}.
        \item Digital Chronicle references: \chron{72}{66}.
    \end{itemize}

    \item \textbf{M7}: \textit{``Address to the National Labor Union of the United States''}
    \begin{itemize}
        \item Original Language: English
        \item Written: 1869, for the GC meeting of May 11; approved.
        \item Dated: May 12. Signed by the GC.
        \item Published: May M, as leaflet pubd by the GC; May 15, in the \textit{Bee-Hive}; May 22, in German, in the \textit{Demokratisches Wochenblatt}.
        \item Source: \textit{GCFI} 3:319 (text of leaflet, with signatures), 101 (\textit{Bee-Hive} text).
        %\item Reprinted: \MESW{2}{156}; ST/M79 (Pad/2) 243; ST/M85 (Pad/3) 102.
        \item Additional Info: In \MEW{16}{355-357}.
        \item Digital Chronicle references: \chron{69}{30}.
    \end{itemize}

    \item \textbf{M8}: \textit{The administration of India and political power in England}. [Untitled article] \{Dubiosa \& Apocrypha\}
    \begin{itemize}
        \item Original Language: English
        \item Published: 1858 Apr 26, in \textit{NYDT}, p. 4de. Lead article; n/s.
        %\item Reprinted: ST/M58 (OCM) 269-71.
        \item Additional Info: Listed by Rubel; rejected by IML; not in \textit{MEW}.
    \end{itemize}

    \item \textbf{M9}: \textit{Advertisement duty—Russian movements—Denmark—The United States in Europe}.
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1853 Aug 5.
        \item Published: Aug 19, in \textit{NYDT}, \#3850, pp. 5f, 6ab, under the rubric ``Great Britain.'' Signed.
        \item Source: \MECW{12}{239}.
        %\item Reprinted: \%ST/M28 (EQ) 87 (``Russian movements—Denmark—U.S. and Europe''); \%ST/ME56 (RME) 173.
        \item Additional Info: In \MEW{9}{245-251}.
        \item Digital Chronicle references: \chron{53}{30}.
    \end{itemize}

    \item \textbf{M10}: \textit{Affairs continental and English}.
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1853 Aug 23.
        \item Published: Sep 5, in \textit{NYDT}, \#3864, p. 6bc. Signed.
        \item Source: \MECW{12}{277}.
        %\item Reprinted: \%ST/M28 (EQ) 118.
        \item Additional Info: In \MEW{9}{286-293}.
        \item Digital Chronicle references: \chron{53}{35}.
    \end{itemize}

%     \item M11: Affairs in France.
%     \begin{itemize}
%         \item Original Language: English
%         \item Dated: 1860 Jan 17.
%         \item Published: Feb 7, in NYDT, \#5862, p. 6bc. N/s.
%         \item Source: \MECW{17}{330}.
%         \item Additional Info: In \MEW{15}{3-7}.
%         \item Digital Chronicle references: \chron{60}{19}.
%     \end{itemize}

%     \item M12: Affairs in Holland—Denmark—Conversion of the British debt—India, Turkey and Russia.
%     \begin{itemize}
%         \item Original Language: English
%         \item Dated: 1853 May 24.
%         \item Published: June 9, in NYDT, \#3790, p. 5ab, under the rubric ``Great Britain.'' Signed.
%         \item Source: \MECW{12}{101}.
%         \item Reprinted: \%ST/M28 (EQ) 27 (``Turkey and Russia''); \%ST/ME56 (RME) 138; \%ST/ME45d (OC) 23 (``India''); \%ST/M58 (OCM) 59 (``The India bill''); \%ST/M3 (AI) 30.
%         \item Additional Info: In \MEW{9}{103-8}.
%         \item Digital Chronicle references: \chron{53}{22}.
%     \end{itemize}

%     \item M13: Affairs in Prussia.
%     \begin{itemize}
%         \item Original Language: English
%         \item Dated: 1858 Oct 16.
%         \item Published: Nov 3, in NYDT, \#5471, p. 6de. N/s.
%         \item Source: \MECW{16}{74}.
%         \item Additional Info: In \MEW{12}{613-616}.
%         \item Digital Chronicle references: \chron{58}{45}.
%     \end{itemize}

%     \item M14: Affairs in Prussia.
%     \begin{itemize}
%         \item Original Language: English
%         \item Dated: 1858: Oct 19.
%         \item Published: Nov 8, in NYDT, \#5475, p. 6ab. N/s.
%         \item Source: \MECW{16}{78}. (++) In MEW 12:617-20.
%         \item Digital Chronicle references: \chron{58}{45}.
%     \end{itemize}

%     \item M15: Affairs in Prussia.
%     \begin{itemize}
%         \item Original Language: English
%         \item Dated: 1858 Nov 16.
%         \item Published: Dec 3, in NYDT, \#5497, p. 6cd. N/s.
%         \item Source: \MECW{16}{106}.
%         \item Additional Info: In \MEW{12}{640-643}.
%         \item Digital Chronicle references: \chron{58}{49}.
%     \end{itemize}

\end{itemize}

%\subsubsection*{Last 15}
\subsubsection*{Last 10}

\begin{itemize}
    % \item M981: The war prospect in France.
    % \begin{itemize}
    %     \item Original Language: English
    %     \item Written: 1859 Mar c.11.
    %     \item Published: Mar 31, in NYDT, \#5598, p. 6de, under the rubric ``France.'' N/s.
    %     \item Source: \MECW{16}{261}.
    %     \item Additional Info: In \MEW{13}{274-279}.
    %     \item Digital Chronicle references: \chron{59}{19}.
    % \end{itemize}

    % \item M982: The war prospect in Prussia.
    % \begin{itemize}
    %     \item Original Language: English
    %     \item Dated: 1859 Mar 15.
    %     \item Published: Mar 31, in NYDT, \#5598, pp. 6f, 7a, under the rubric ``Germany.'' N/s.
    %     \item Source: \MECW{16}{267}.
    %     \item Additional Info: In \MEW{13}{280-283}; this article followed \#M981.
    %     \item Digital Chronicle references: \chron{59}{19}.
    % \end{itemize}

    % \item M983: The war question—British population and trade returns—Doings of Parliament.
    % \begin{itemize}
    %     \item Original Language: English
    %     \item Dated: 1853 Aug 12.
    %     \item Published: Aug 24, in NYDT, \#3854, pp. 5ef, 6a. Signed; Aug 27, shortened, in Die Reform.
    %     \item Source: \MECW{12}{245}.
    %     \item Reprinted: \%ST/M28 (EQ) 92 (``To withdraw or not to withdraw''); \%ST/ME28 (I1Q) 67.
    %     \item Additional Info: In \MEW{9}{252-264}.
    %     \item Digial Chronicle references: \chron{53}{30}.
    % \end{itemize}

    % \item M984: The war question—Doings of Parliament—India.
    % \begin{itemize}
    %     \item Original Language: English
    %     \item Dated: 1853 July 19.
    %     \item Published: Aug 5, in NYDT, \#3838, p. 6ab. Signed.
    %     \item Source: \MECW{12}{209}.
    %     \item Reprinted: \%ST/M28 (EQ) 71 (``Russia and the western powers''); \%ST/ ME56 (RME) 162; \%ST/ME45d (OC) 72 (``India''); \%ST/M58 (OCM) 121 (``Indian affairs''); \%ST/M102 (SFE) 316 (do.).
    %     \item Additional Info: In \MEW{9}{212-219}.
    %     \item Digital Chronicle references: \chron{53}{30}.
    % \end{itemize}

    % \item M985: The war question—Financial matters—Strikes.
    % \begin{itemize}
    %     \item Original Language: English
    %     \item Dated: 1853 Oct 7.
    %     \item Published: Oct 21, in NYDT, \#3904, p. 6ab, under the rubric ``Great Britain.'' Signed; Oct 24, 25, shortened, in Die Reform, in German, ``Die Lage in England'' [The situation in England].
    %     \item Source: \MECW{12}{407}.
    %     \item Reprinted: \%ST/M28 (EQ) 142 (``The war question'').
    %     \item Additional Info: In \MEW{9}{419-427}.
    %     \item Digital Chronicle references: \chron{53}{40}.
    % \end{itemize}

    \item \textbf{M986}: \textit{War—Strikes—Dearth}.
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1853 Nov 1.
        \item Published: Nov 15, in \textit{NYDT}, \#3925, pp. 5f. 6ab, under the rubric ``England.'' Signed.
        \item Source: \MECW{12}{435}.
        %\item Reprinted: \%ST/M28 (EQ) 150 (``War'').
        \item Additional Info: In \MEW{9}{447-455}.
        \item Digital Chronicle references: \chron{53}{44}.
    \end{itemize}

    \item \textbf{M987}: \textit{Warning}.
    \begin{itemize}
        \item Original Language: German
        \item Title in Original Language: \textit{Warnung}.
        \item Dated: 1866 May 4.
        \item Published: May 15, in the \textit{Oberrheinischer Courier}; also in other German papers. Signed by M on behalf of the GC.
        \item Source: \MEW{16}{164-165}; \textit{GCFI} 1:335.
        %\item Translations: GCFI 1:367.
        \item Digital Chronicle references: \chron{66}{23}.
    \end{itemize}

    \item \textbf{M988}: \textit{The Washington cabinet and the western powers}.
    \begin{itemize}
        \item Original Language: German
        \item Title in Original Language: \textit{Das Kabinett von Washington und die Westmächte}.
        \item Written: 1861 Dec c.20.
        \item Published: Dec 25, in \textit{Die Presse}. N/s.
        \item Source: \MEW{15}{427-429}.
        %\item Translations: ST/ME10c (CWUS) 120; ST/M79 (Pad/2) 135.
        \item Digital Chronicle references: \chron{61}{54}.
    \end{itemize}

    \item \textbf{M989}: \textit{The western powers and Turkey--Symptoms of economic crisis}. [Untitled]
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1853 Sep 23.
        \item Published: Oct 7, in \textit{NYDT}, \#3892, p. 6abc. Signed.
        \item Source: \MECW{12}{318}.
        %\item Reprinted: \%ST/M28 (EQ) 134 (``The English ministry outwitted—Panic'').
        \item Additional Info: In \MEW{9}{330-340}. On the economic part, M used material sent by E.
        \item Digital Chronicle references: \chron{53}{40}.
    \end{itemize}

    \item \textbf{M990}: \textit{The western powers and Turkey---Imminent economic crisis---Railway construction in India}. [Untitled]
    \begin{itemize}
        \item Original Language: English
        \item Dated: 1853 Sep 20.
        \item Published: Oct 4, in \textit{NYDT}, \#3889, pp. 5f, 6ab. Signed.
        \item Source: \MECW{12}{309}.
        %\item Reprinted: \%ST/M28 (EQ) 128 (``The Vienna note continued'').
        \item Additional Info: In \MEW{9}{321-329}.
        \item Digital Chronicle references: \chron{53}{40}, \chron{53}{41}.
    \end{itemize}

    \item \textbf{M991}: \textit{What has Italy gained?}
    \begin{itemize}
        \item Original Language: English
        \item Written: 1859 July c.12.
        \item Published: July 27, in \textit{NYDT}, \#5697, p. 4ab. Lead article; N/s.
        \item Source: \MECW{16}{407}.
        \item Additional Info: In \MEW{13}{417-419}.
        \item Digital Chronicle references: \chron{59}{52}.
    \end{itemize}

    \item \textbf{M992}: \textit{Wild songs}.
    \begin{itemize}
        \item Original Language: German
        \item Title in Original Language: \textit{Wilde Lieder. [Poems]}
        \item Written: 1837 prob Feb to (at latest) Apr A, for the original versions. This was the overall title used on publication for two poems---``The Minstrel'' [Der Spielmann] and ``Love in the night'' [Nachtliebe]---both of which were in \register{M663}, q.v.
        \item Published: 1841 Jan 23, in \textit{Athenäum} (Berlin), no. 4, p. 59; text somewhat revised. Signed: K. Marx.
        \item Source: \MEW{40}{604-605}; \oldmega{I}{1.1}{147}; \MEGA{I}{1}{768}; all the foregoing presenting the pubd version. For the original version, see \oldmega{I}{1.2}{9, 57}; or \MEGA{I}{1}{626, 670}.
        %\item Translations: \MECW{1}{22} (pubd version); ST/14 (KMTR) 1:610 (both versions); R. Payne, Marx, p. 62 (garbled trans).
        \item Additional Info: These poems were the first things pubd by M, and were the only poems pubd by him.
        \item Digital Chronicle references: \chron{37}{4}; \chron{41}{4}.
    \end{itemize}

    \item \textbf{M993}: \textit{Workers' distress in England}.
    \begin{itemize}
        \item Original Language: German
        \item Title in Original Language: \textit{Die Arbeiternot in England}.
        \item Written: 1862 Sep c.20.
        \item Published: Sep 27, in \textit{Die Presse}. N/s.
        \item Source: \MEW{15}{544-547}.
        \item Digital Chronicle references: \chron{62}{49}.
    \end{itemize}

    \item \textbf{M994}: \textit{A workers' inquiry}.
    \begin{itemize}
        \item Original Language: French
        \item Title in Original Language: Enquête ouvrière.
        \item Written: 1880 Apr AB, in English (see note below).
        \item Published: Apr 20, in French, in the \textit{Revue Socialiste}; titled as at head; N/s.; Then reprinted separately, and circulated through France.
        \item Source: \register{ST/M78} (Oeuvres) 1:1529.
        %\item Translations: New International (NY), Dec 1938; a pamphlet reprint of this trans was pubd in Ceylon, 1955. Also a pamphlet, titled A workers' enquiry, pubd in London by CPGB, 1933.
        \item Additional Info: In \MEW{19}{230-237}. The \textit{MEW} version is transd from the English-language ms (which has not been pubd, as far as I know). It is not stated whether \textit{MEW}'s title, ``Fragebogen für Arbeiter'' [Questionnaire for workers], is based on M's ms or on M's letter to Sorge of Nov 5, where he calls it a questionneur (questioner).
        \item Digital Chronicle references: \chron{80}{13}.
    \end{itemize}

    \item \textbf{M995}: \textit{Yet another word on ``Bruno Bauer und die akademische Lehrfreiheit by Dr. O. F. Gruppe, Berlin, 1842.''}
    \begin{itemize}
        \item Original Language: German
        \item Title in Original Language: \textit{Noch ein Wort über ``Bruno Bauer und die akademische Lehrfreiheit von Dr. O. F. Gruppe. Berlin 1842.''}
        \item Written: 1842 Sep A.
        \item Published: Nov 16, in the \textit{Deutsche Jahrbücher für Wissenschaft und Kunst}. Signed: K.M.
        \item Source: \MEW{40}{381-384}; \oldmega{I}{1.1}{397}.
        %\item Translations: \MECW{1}{211}; ST/M83 (Pad/5) 27.
        \item Digital Chronicle references: \chron{42}{24}, \chron{42}{31}.
    \end{itemize}

\end{itemize}

The additional \register{} entries referenced by the records above are as follows:

\begin{itemize}
    \item \textbf{M945}: \textit{The Trial of Simon Bernard} [Untitled] \{Dubiosa \& Apocrypha\}
    \begin{itemize}
        \item Original Language: English
        \item Published: 1858 Apr 30, in \textit{NYDT}, p. 4cd. Lead article; N/s.
        \item Additional Info: Listed by Rubel; rejected by IML, not in \textit{MEW}. In my opinion, this is not by M; the case is similar to that of \register{M4}, q.v.
    \end{itemize}
    \item \textbf{ST/ME10c}: \textit{The Civil War in the United States}. 3rd Ed. Ed by Richard Enmale. Int'l Pub, Citadel Pr., 1961. 334p.
    \item \textbf{ST/M78}: \textit{Oeuvres. Economie.} Edition établie et anotée par Maximilien Rubel. Préface par François Perroux. (Bibliothèque de la Pléiade) 2v. Paris: Gallimard, 1965, 1968.
    \item \textbf{ST/M79}: \textit{On America and the Civil War}. (Karl Marx Lib, 2). Arranged and ed, with an intro and a new trans, by Saul K. Padover. NY: McGraw-Hill, 1972. 298p.
    \item \textbf{ST/M80}: \textit{On Education, Women, and Children}. (Karl Marx Lib, 6). Arranged and ed, with an intro and a new trans, by Saul K. Padover. NY: McGraw-Hill, 1975. 164p.
    \item \textbf{ST/21}: \textit{The General Council of the First International}... (Documents of the First International). FLPH/Progress Publishers, n.d. [1963-1968?].
    \begin{itemize}
        \item Five unnumbered volumes, issued by the IML, Moscow. Prefaces in each volume unsigned. In the \textit{Register}, volume numbers have been assigned; following are the conferred volume numbers and the subtitles:
        \item Vol. 1. ...\textit{1864-1866. The London Conference 1865. Minutes.} FLPH, n.d. [1963?].
        \item Vol. 2. ...\textit{1866-1868. Minutes.} Progress Publishers, n.d.
        \item Vol. 3. ...\textit{1868-1870. Minutes.} Progress Publishers, n.d.
        \item Vol. 4. ...\textit{1870-1871. Minutes.} Progress Publishers, n.d.
        \item Vol. 5. ...\textit{1871-1872. Minutes.} Progress Publishers, n.d. [1968?]
    \end{itemize}
\end{itemize}

And the abbreviations used throughout the above entries are as follows:

\begin{enumerate}
    \item[A] (After a month, e.g., Sep A) The first quarter of the month
    \item[AB] (After a month, e.g., Sep AB) The first half of a month
    \item[c.] (In front of dates) Circa; approximately
    \item[CWUS] \textit{The Civil War in the United States}, Ed. Richard Enmale (\register{ST/ME10c})
    \item[FLPH] Foreign Languages Publishing House (Moscow)
    \item[GC] General Council (of the IWMA)
    \item[GCFI] \textit{General Council of the First International} (\register{ST/21})
    \item[IML] \textit{Institut für Marxismus-Leninismus} (Referring either to the \textit{Institut Marksizma-Leninizma} in Moscow or the \textit{Institut für Marxismus-Leninismus} in East Berlin, depending on context)
    \item[IWMA] International Working Men's Association
    \item[N/s] Not signed
    \item[NYDT] \textit{New York Daily Tribune}
    \item[Pad/$N$] Saul K. Padover's \textit{Karl Marx Library} series, volume $N$.
    \item[pubd] Published
    \item[q.v.] ``On which, see''
    \item[ST] (In record code, e.g., ST/M60) Sources and Translations
    \item[transd] Translated
    \item[\%] Denotes that the source immediately following contains only a \textit{partial} translation of the text of interest
\end{enumerate}

%, password ``\texttt{mega2021}''
